---
title: 'Exercise #6'
author: "Ella Bauer (11927761), Maxi Böck (12466170)"
date: "`r Sys.Date()`"
output:
  distill::distill_article
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2022/23"
---

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.
-   Make sure to submit you render your Rmarkdown as
    `distill:distill_article` and check the final output regarding any
    issues in formatting. Formatting errors may lead to point
    deductions.

## Exercise 1: Building an R package (20 Points)

For this exercise we ask you to build an R package. We do not ask you to
build any particular R package, but leave the choice of what your R
package will do up to you, to keep it more interesting for you.

Instead of having particular tasks for you to complete, we have a list
of requirements for your final R package and submission. Please submit
an Rmd and render it as always, although you will only have to provide
the short information asked for under *Submission*.

We advise you to start early with this exercise sheet and encourage you
to reach out if you encounter issues during the creation of your
package. For detailed information on all aspects of creating an R
package, we highlight again, the [great book on R
packages](https://r-pkgs.org/) by Hadley Wickham.

We look forward to seeing the cool packages you come up with and thank
you for participating in the course!

### Submission

a)  Briefly describe in one sentences what your R package does and why
    you decided to choose this functionality. This is just intended to
    give us some context to better understand the package.
    
I enjoy working with text, so I created a text mining package with the basic purpose of counting all words in a given text. To achieve this, I developed two text cleaning functions and a word counting function.
    
    
b)  To make installation easier, your R package should be in a public
    repository on GitHub. Provide the URL to the GitHub repository
    below:

https://github.com/MaxiBoeck/Excersice-6.git

c)  Your R package should be installable via
    `remotes::install_github()`. Before submitting your solution to this
    exercise sheet please test whether you can install your R package
    from GitHub. Provide the command below:
    
```{r}
remotes::install_github("https://github.com/MaxiBoeck/Excersice-6.git")
```

### Functionality

a)  Create a working R package that performs the task it is intended to
    do

b)  Your R package needs to be installable (test this before submitting)

c)  Your R package should contain at least 2 functions

d)  The functions in your R package should be properly documented
    according to the Roxygen convention. Each function should include an
    `@example` tag.

e)  The documentation for your package should be properly generated and
    up-to-date. After every change to the Roxygen comments of your
    functions, you will need to run `devtools::document()` again to do
    this.
```{r}
library(devtools)
devtools::document()
```

f)  The `DESCRIPTION` file of your package should be properly formatted
    and contain all the required dependencies of your package. It should
    also provide an accurate `Title` and `Description` for your package.
    


```{r}
create_package("C:/Users/MaxiB/Desktop/FortStat Abgabe/Excersise Sheet 6/Excersice6")
```
    
    
```{r}

# Text Input (just replace with your text between the qotation marks. Works best with Blocktext without qotation marks. You can use English or German texts. This example text is from Chatgpt)
text <- "Once upon a time, in a small village nestled between rolling hills and lush forests, there lived a young girl named Lily. She had a heart as pure as the morning dew and a spirit as free as a bird in flight. Lily spent her days exploring the wonders of nature, climbing trees, and chasing butterflies. One sunny morning, while wandering through the woods, Lily stumbled upon a hidden glade filled with colorful wildflowers. Mesmerized by the beauty around her, she decided to pick a bouquet of the loveliest blooms as a gift for her grandmother. As she made her way back to the village, she encountered an injured bird lying helplessly on the ground. Without a second thought, Lily carefully scooped up the delicate creature and cradled it in her hands. Determined to help, she rushed to her grandmother's cottage, seeking her wisdom and healing touch. Her grandmother, a wise woman with a deep connection to nature, examined the injured bird and gently mended its wing. As Lily watched in awe, the bird's eyes met hers, and in that moment, she felt an inexplicable bond between them. With the bird now on the path to recovery, Lily continued her journey back to the village. Along the way, she met a group of children playing by the river. They were amazed by the beauty of the wildflowers she carried and asked her about her adventures in the woods. Lily, always eager to share her love for nature, regaled them with stories of her encounters with animals and the wonders of the forest. The children listened with rapt attention, hanging onto her every word. From that day on, Lily became known as the village's little nature ambassador. She would lead nature walks, teach her friends about different plants and animals, and inspire everyone with her boundless curiosity and kindness. As the years passed, Lily's love for nature only grew stronger. She vowed to protect the environment and all its creatures, cherishing the beauty that surrounded her. And so, the young girl with the heart of gold and the soul of a free spirit continued to spread love and harmony wherever she went."

library(Excersice.6)
cleaned_text <- clean_text(text)
print(cleaned_text)
filtered_text <- remove_stopwords(cleaned_text)
print(filtered_text)
word_count <- count_words(filtered_text)
print(word_count)
```
